I owe an immeasurable amount of thanks to my advisor Alex Shkolnik---for without him---I would not have been able to complete my thesis.
He served as a great resource for finding important publications, offered a lot of intuition on the subject, and motivated purpose in the dismal moments of research.
I am very grateful for his patience, openness, and positivity.
He was never shy to compliment me when a result was established, and I always felt comfortable to tell him when progress was slow.
His ability to adopt new perspectives made research exciting, and our discussions always felt humble and productive.
To me, the comfort of discussion with minimal social barrier is very important, and he could not have been a better advisor in this manner.
Lastly, he respected that I have a life outside of research---even if it got in the way of timely results, I was able to explore hobbies and bond with family and friends, knowing I had his empathy.

Although the complete work of my thesis was done with Alex, my mathematics learning has a far longer history that extends many years back.
I have been very lucky to have handfuls of helpful and encouraging professors in my time, and their excitement in mathematics helped me develop the skills I have today.

Aside from the tools I have used to write this thesis, I unashamedly admit I have needed so much other support from loved ones, to which I owe the greatest thanks.
I would like to fill a book expressing my gratitude to all the great things in my life, but this would take up the majority of my thesis!
Instead, I will shortly list those who have made a significant impact in my studies.
I would like to give thanks to my friends Niklas Griessbaum and Jeff Inglis; the countless laughs, arguments, and acts of support these two have shared with me are of the highest importance.
Also, their wisdom and inspiration have helped me grow so much as a person.
I am grateful for the support, honesty, and candid acceptance of Amanda Huntington---especially during the early years of research, when I still greatly lacked confidence.
Emily Jensen was the best colleague I can ask for, and I am so happy to have spent so many hours talking math and life with her.
I owe so much to Sam and Eric---through them, I obtained a thrill to live and persevere through life's hardest times.
Finally, even though she only saw the very end of my studies, I give great thanks to Kaitlynne Henney for being so accommodating and loving during the stressful period of writing of my thesis.

Lastly, with any event of my life, I will always owe the most thanks to my loving parents, Shawn and Kimberly Varble.
Their love is fundamentally the most accountable thing in my life, and I don't know where I would be without it.
I could not have asked for better parents, and to them, I will always owe my greatest thanks.
If there is anything that motivates me, it is the will to show them how far their love and support can take me.
I will do just about anything to make them proud and return the immense love and support they give me.
