% formulate jump-diffusions in terms of characteristics
As in \cite[Definition III.2.18]{jacod2003}, a $(\Prb, \scrF)$ jump-diffusion $\X$ on state space $(\stateSpace, \scrB(\stateSpace))$ is a $(\Prb, \scrF)$ semimartingale in which the $\trunc$-characteristics $(B^\trunc, A, \predproj{\jumpMeas^\X})$ have the following decompositions,
\begin{equation}
  \label{eq:jump-diffusion-characteristics}
  B^\trunc_t = \int_0^t \affDrift^\trunc(\X_s) \rmd s, \quad 
  A_t = \int_0^t \affDiff(\X_s) \rmd s, \quad
  \predproj{\jumpMeas^\X}(\rmd s,\rmd\markVar) = \affJump(\X_s, \rmd\markVar) \rmd s,
\end{equation}
where the functions have the following properties.
\begin{itemize}
  \item
    $\affDrift^\trunc: \stateSpace \rightarrow \vecSpace$ is Borel measurable, $\affDrift^\trunc \in \scrB(\stateSpace)/\scrB(\vecSpace)$.
  \item
    $\affDiff: \stateSpace \rightarrow \bbL(\vecSpace)$ is Borel measurable, $\affDiff \in \scrB(\stateSpace)/\scrB(\bbL(\vecSpace))$, and $\affDiff(\stateVar)$ is self-adjoint and nonnegative for each $\stateVar \in \stateSpace$.
  \item
    $\affJump: \stateSpace \times \scrB(\vecSpace) \rightarrow [0,\infty]$ is a transition kernel from $\stateSpace$ to $\vecSpace$, and it satisfies the following properties for each $\stateVar \in \stateSpace$.
    \[
      \affJump\big(\stateVar, \{0\}\big) = 0, \quad \int_\vecSpace \big( 1 \wedge |\markVar|^2\big) \affJump(\stateVar, \rmd\markVar) < \infty
    \]
\end{itemize}
In other words, our jump-diffusion $\X$ has the following canonical semimartingale representation (see \cite[Theorem II.2.34]{jacod2003} for definition).
\begin{equation}
  \label{eq:jump-diffusion-canonical}
  \begin{gathered}
    \X = \X_0 + \affDrift^\trunc(\X) \shortInt \leb + \X^\rmc +  \trunc \ast \compensate{\jumpMeas^\X} + (\id_\vecSpace - \trunc) \ast \jumpMeas^\X \\
    \prj{\X^{\rmc,i}}{\X^{\rmc,j}} = \affDiff_{ij}(\X) \shortInt \leb \\
    \predproj{\jumpMeas^\X}(\rmd s, \rmd\markVar) = \affJump(\X_s, \rmd\markVar) \rmd s
  \end{gathered}
\end{equation}

% a quick remark on differences and terminology.
\input{./results/definition-remarks}

% a quick example to demonstrate Brownian motion and Poisson.
\input{./results/example}

The following Lemma will be repeatedly used as a shortcut of It\^o's formula and various identities that always apply with jump-diffusions.

% restate Ito in terms of jump-diffusions
\input{./results/ito}

% express the notion of the generator of X
In the above lemma, the final term in the semimartingale decomposition of $f(\X)$ is typically not able to be compensated into a local martingale.
If we did have local integrability of the following quantity,
\begin{equation*}
  \Big| f(\X_-+\id_\vecSpace) - f(\X_-) + \Der f(\X_-) \cdot \trunc \Big| \ast \predproj{\jumpMeas^\X},
\end{equation*}
then by \cite[Proposition II.1.28]{jacod2003} we could rewrite $f(\X)$ into a canonical special semimartingale decomposition.
\begin{equation}
  \label{eq:jump-diffusion-generator}
  \begin{aligned}
    f(\X_t) &= f(\X_0) + \generator f(\X) \shortInt \leb_t + \Der f(\X_-) \shortInt \X^\rmc + \big( f(\X_- + \id_\vecSpace) - f(\X_-) \big) \ast \compensate{\jumpMeas^\X}_t \\
    \generator f(\stateVar) &\defeq \begin{aligned}[t]
      &\Der f(\stateVar) \cdot \affDrift^\trunc(\stateVar) + \frac12 \tr\Big( \Hess f(\stateVar) \circ \affDiff(\stateVar) \Big) \\
      &\hspace{25mm}+ \int_\vecSpace \Big( f(\stateVar + \markVar) - f(\stateVar) - \Der f(\stateVar) \cdot \trunc(\markVar) \Big) \affJump(\stateVar, \rmd\markVar)
    \end{aligned}
  \end{aligned}
\end{equation}
So long as $f$ is bounded, we can guarantee this special semimartingale property.

% bounded
\input{./results/ito-bounded}

This operator $\generator$ in (\ref{eq:jump-diffusion-generator}) gives a nice closed from for suitable $f(\X)$, and so we reserve it the term of \emph{generator} associated with $\X$.
Note that we do not mark dependence on $\trunc$, as any other truncation function $\hat\trunc$ will produce the same operator; see Remark \ref{remark:jump-diffusions}\ref{remark:characteristic-switch} and note that the displacement from $\affDrift^\trunc$ and $\affDrift^{\hat\trunc}$ would be the same as that in the integral term.
One particular setting in which this result is useful is establishing a L\'evy-Khintchine formula for jump-diffusions.

% Levy-Khintchine
\input{./results/LK}

% manifest equivalence
It turns out that each of the preceding results is sufficient in characterizing a semimartingale $\X$ as a jump-diffusion.

\input{./results/characterizations}
